Probabilities of polar alignment in circumbinary disks

### 2024-12-17 src/tex/ms.tex
use rin/ab = 2.5

If we consider a $p=1$ disk orbiting an equal mass binary with $e_\text{b}=0.4$ and $r_\text{in}/a_\text{b}=5$, then for a relatively thin ring ($r_\text{out}/r_\text{in} = 2$), we calculate $j_\text{max} = 0.24$. If the disk is allowed to be more extended (in this case $r_\text{out}/r_\text{in} = 10$), then we find $j_\text{max} = 4.0$.

@@

Note that equation (\ref{eq:jmax-steep}) is less than equation ({\ref{eq:jmax-shallow}}) by a factor of $(r_\text{out}/r_\text{in})^{2-p}$. If we consider the same example as in Section \ref{subsubsec:shallow-p}, except with $p=3$, we find that in the thin case ($r_\text{out}/r_\text{in} = 2$), $j_\text{max} = 0.057$, and is even smaller for $r_\text{out}/r_\text{in} = 10$, at  $j_\text{max} = 0.027$.

\subsubsection{$p=2$}
Equations (\ref{eq:jmax-shallow} \& \ref{eq:jmax-steep}) are equivalent when $p=2$, and both analyses are equally valid. The qualitative change that occurs when $p=2$ is that instability does not onset at either disk edge, but is independent of radius and occurs everywhere simultaneously. Again, following the example parameters listed above, we find that $j_\text{max} = 0.16$ for $r_\text{out}/r_\text{in} = 2$ and $j_\text{max} = 0.84$ for $r_\text{out}/r_\text{in} = 10$.

>>>>

If we consider a $p=1$ disk orbiting an equal mass binary with $e_\text{b}=0.4$ and $r_\text{in}/a_\text{b}=2.5$, then for a relatively thin ring ($r_\text{out}/r_\text{in} = 2$), we calculate $j_\text{max} = 0.17$. If the disk is allowed to be more extended (in this case $r_\text{out}/r_\text{in} = 10$), then we find $j_\text{max} = 2.8$.

@@

Note that equation (\ref{eq:jmax-steep}) is less than equation ({\ref{eq:jmax-shallow}}) by a factor of $(r_\text{out}/r_\text{in})^{2-p}$. If we consider the same example as in Section \ref{subsubsec:shallow-p}, except with $p=3$, we find that in the thin case ($r_\text{out}/r_\text{in} = 2$), $j_\text{max} = 0.040$, and is even smaller for $r_\text{out}/r_\text{in} = 10$, at  $j_\text{max} = 0.019$.

\subsubsection{$p=2$}
Equations (\ref{eq:jmax-shallow} \& \ref{eq:jmax-steep}) are equivalent when $p=2$, and both analyses are equally valid. The qualitative change that occurs when $p=2$ is that instability does not onset at either disk edge, but is independent of radius and occurs everywhere simultaneously. Again, following the example parameters listed above, we find that $j_\text{max} = 0.11$ for $r_\text{out}/r_\text{in} = 2$ and $j_\text{max} = 0.60$ for $r_\text{out}/r_\text{in} = 10$.
